---
title: "Zero Knowledge Traders"
author: "Ernesto Carrella"
date: "11/07/2014"
output: beamer_presentation
---


## Zero Knowledge Traders

- Simple firms:
    - Price-Makers
    - No knowledge of output demand
    - No knowledge of labor supply
    - No knowledge of competition
    - Only know own daily sales
    
- Price by trial and error
    - Find price so that production = sales
    - Use PID controller to adjust  

- Set production quota by trial and error
    - Look for MB=MC
    - Use Kalman Filter to learn elasticities over time

## 1 Monopolist

```{r, echo=FALSE,message=FALSE,warning=FALSE}
library(ggplot2)
library(reshape2)
library(gridExtra)
monopolist<-read.csv("./rawdata/monopolist.csv")
plot_price<-
  ggplot()+
  geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=78.5,ymax=79.5,fill=factor(1)),alpha=0.3) +
  geom_line(data=monopolist,aes(x=1:length(CLOSING_PRICE),y=CLOSING_PRICE)) +
  ylab("Price") + xlab("Days") + 
  theme_gray(20)+guides(colour = guide_legend(override.aes = list(size=3))) + #   scale_y_continuous(breaks=breaks_y,minor_breaks=1:70) +
  scale_fill_manual(values="blue",labels="Correct P",name="") +
  theme(axis.text.y = element_text(size=20)) +   theme(axis.text.x = element_text(size=20)) +
    scale_y_continuous(breaks=c(0,25,50,79,100)) +
  coord_cartesian(xlim=c(0,5000),ylim=c(0,105)) 
#print(plot_price)

plot_quantity<-
  ggplot()+
  geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=21.5,ymax=22.5,fill=factor(1)),alpha=0.3) +
  geom_line(data=monopolist,aes(x=1:length(VOLUME_PRODUCED),
                                y=VOLUME_PRODUCED)) +
  ylab("Production") + xlab("Days") + 
  theme_gray(20)+guides(colour = guide_legend(override.aes = list(size=3))) + #   scale_y_continuous(breaks=breaks_y,minor_breaks=1:70) +
  scale_fill_manual(values="blue",labels="Correct Q",name=" ") +
  theme(axis.text.y = element_text(size=20)) +   theme(axis.text.x = element_text(size=20)) +  
  scale_y_continuous(breaks=c(0,5,10,15,22,25)) +
  coord_cartesian(xlim=c(0,5000))
#print(plot_quantity)
arranged2Plots<-function(plot1,plot2,main=NULL)
{
  gA <- ggplotGrob(plot1)
  gB <- ggplotGrob(plot2)
  maxWidth = grid::unit.pmax(gA$widths[2:5], gB$widths[2:5])
  gA$widths[2:5] <- as.list(maxWidth)
  gB$widths[2:5] <- as.list(maxWidth)
  return(grid.arrange(gA, gB, ncol=1,main=textGrob(main,gp=gpar(fontsize=30))))
}
arranged2Plots(plot_price,plot_quantity,main="Monopolist Sample Run")
```

- 2 markets: output and labor. Firm is monopolist in both.

## 5 competitors

```{r, echo=FALSE,message=FALSE,warning=FALSE}
library(ggplot2)
library(reshape2)
library(gridExtra)
competitive<-read.csv("./rawdata/competitive.csv")
plot_price<-
  ggplot()+
  geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=78.5,ymax=79.5,fill=factor(1)),alpha=0.3) +
  geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=57.5,ymax=58.5,fill=factor(2)),alpha=0.3) +
  geom_line(data=competitive,aes(x=1:length(CLOSING_PRICE),y=CLOSING_PRICE),lwd=1) +
  ylab("Price") + xlab("Days") + 
  theme_gray(20)+guides(colour = guide_legend(override.aes = list(size=3))) + #   scale_y_continuous(breaks=breaks_y,minor_breaks=1:70) +
  scale_fill_manual(values=c("blue","red"),labels=c("Monopolist P","Competitive P"),name=" ") +
  theme(axis.text.y = element_text(size=20)) +   theme(axis.text.x = element_text(size=20)) + 
  scale_y_continuous(breaks=c(seq.int(from=0,to=100,by=25),58)) +  
  coord_cartesian(xlim=c(0,4000),ylim=c(0,105)) 
#print(plot_price)

plot_quantity<-
  ggplot()+
  geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=21.5,ymax=22.5,fill=factor(1)),alpha=0.3) +
  geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=43.5,ymax=44.5,fill=factor(2)),alpha=0.3) +    
  geom_line(data=competitive,aes(x=1:length(VOLUME_TRADED),
                                y=VOLUME_TRADED),lwd=1) +
  ylab("Production") + xlab("Days") + 
  theme_gray(20)+guides(colour = guide_legend(override.aes = list(size=3))) + #   scale_y_continuous(breaks=breaks_y,minor_breaks=1:70) +
  scale_fill_manual(values=c("blue","red"),labels=c("Monopolist Q","Competitive Q"),name=" ") +
  theme(axis.text.y = element_text(size=20)) +   theme(axis.text.x = element_text(size=20)) +  
  scale_y_continuous(breaks=c(seq.int(from=0,to=60,by=20),44)) +
  coord_cartesian(xlim=c(0,4000))
#print(plot_quantity)
library(gridExtra)
arranged2Plots<-function(plot1,plot2,main=NULL)
{
  gA <- ggplotGrob(plot1)
  gB <- ggplotGrob(plot2)
  maxWidth = grid::unit.pmax(gA$widths[2:5], gB$widths[2:5])
  gA$widths[2:5] <- as.list(maxWidth)
  gB$widths[2:5] <- as.list(maxWidth)
  return(grid.arrange(gA, gB, ncol=1,main=textGrob(main,gp=gpar(fontsize=30))))
}

arranged2Plots(plot_price,plot_quantity,main="Competitive Sample Run")
```
- Same setup, now with 5 firms.They aren't "told" they have competitors. They learn it.
